%\subsection{ACADEMIC}

\subsection{Peer Reviewed Research Papers}
 \begin{enumerate}
 
       \item \textbf{Carrera, Dashiel}, Kaur, Jasmine, Kapoor, Daksh, Zhang, Chengzhi, Kim, Jisu, Brian Magerko. ``'Jaw Dropping' Sound Clouds: Exploring the Role of Awe and Perceived Comprehension in Ambient Computational Systems." In Proceedings of the ACM Conference on Creativity \& Cognition \textbf{(C\&C)}. London, England 2026.  \\
 
     \item \textbf{Carrera, Dashiel}, Thomas-Mitchell, Jeb, Daniel Wigdor. ``'Where Do I Add the Egg?': Exploring Agency and Ownership in AI Creative Co-Writing Systems." In Proceedings of the ACM Conference on Human Factors in Computing Systems \textbf{(CHI)}. Barcelona, Spain 2026.\\
 
  
  \item \textbf{Carrera, Dashiel}, Zhao, Zixin, Ajin Thomas, Ashish, Daniel Wigdor. ``Nabokov's Cards: An AI Assisted Prewriting Systems to Support Bottom-Up Creative Writing." In Proceedings of the ACM Conference on Creativity \& Cognition \textbf{(C\&C)}. London, England 2025. \\
  \item \textbf{Carrera, Dashiel}, Bhattacharjee, Gitanjali, Robert Soden. ``We're Not Decorators: Understanding Art-Science Collaboration Through Artist in Residency Programs in STEM Organizations." In Proceedings of the ACM Conference on Design of Interactive Systems \textbf{(DIS)}. Pittsburgh, Pennsylvania 2023. \\
  \item \textbf{Carrera, Dashiel}, Ovienmhada, Ufuoma, Hussein, Safa, and Robert Soden. ``The Unseen Landscape of Abolitionism: Examining the role of digital maps in
grassroots organizing."   In Proceedings of the ACM Conference on Computer Supported Cooperative Work \textbf{(CSCW)}. Minneapolis, Minnesota 2023.\\
  \item \textbf{Carrera, Dashiel}, Lee, Sang Won. ``Watch Me Write: Revealing Creative Process with Writing Replay" In Proceedings of the ACM Conference on Creativity \& Cognition \textbf{(C\&C)}. Venice, Italy 2022. \\
  \item Thompson, Tyechia, \textbf{Carrera, Dashiel}. ``Afrofuturist Intellectual Mixtapes: A Classroom Case Study" In Digital Humanities Quarterly \textbf{(DHQ)}. Boston, MA, 2021.\
 \end{enumerate}
 
% \subsection{Full Papers on Submission}
 
%  \begin{enumerate}
 

      
  %     \item \textbf{Carrera, Dashiel}, Zhao, Zixin, Halperin, Brett, Kreminski, Max, Chakrabarty, Tuhin, Lydia Chilton. ``AI Narratives of Provenance: Examining the Role of Narrative in AI Co-writing Disclosure." In Proceedings of the ACM Conference on Creativity \& Cognition \textbf{(C\&C)}. London, England 2026.  \\
        
  
% \item \textbf{Carrera, Dashiel}, Kalirai, Manveer, Fernandes, Kim, Levine, Rachel, Soden, Robert, Daniel Wigdor. ``The AI Metaphors Workshop: Creating New Interface Metaphors for LLMs through a Collaborative Workshop with Artists." In New Metaphors for Artificial Intelligence, 2027.  \\

%\item Kaur, Jasmine, Alvarenga Medina, Angelina Thais, Kapoot, Daksh, Zhang, Chengzhi, Kim, Jisu, Shin, Hyunkyung, \textbf{Carrera, Dashiel}, Brian Magerko. ``Computing in the Sound Clouds: Inflatable Interfaces for Ambient Awe." In TEI Pictorial. Chicago, IL 2026. (under submission) \\

  %\end{enumerate}
 

\subsection{Lightly Reviewed and Workshop Papers}
\begin{enumerate}

\item Zhang, Chengzhi, \textbf{Carrera, Dashiel*}, Kapoor, Daksh*, Kapoor, Jasmine*, Kim, Jisu*, Brian Magerko. ``Sound Clouds - Exploring ambient intelligence in public spaces to elicit deep human experience of awe, wonder, and beauty." In NeurIPS Creative AI Track. San Diego, CA 2025.

 \item Brand, Amy, \textbf{Carrera, Dashiel}, Gero, Katy, and Susan Silbey. ``Who Controls Knowledge in the Age of AI?" In Scholarly Kitchen. Wheat Ridge, CO 2025. \\
 \item Agrawaa, Taneea, Bonfils, Nils, Wi, Siyi, Lee Dogan, Amelia, \textbf{Carrera, Dashiel}. ``The Toronto Water Atlas," COMPASS Art and Demos. Toronto, ON 2025. \\
 \item \textbf{Carrera, Dashiel}. ``AI Baby Jesus: Using a Design Metaphor for AI to Explore Design Fiction," HCI Design Stories CHI Workshop. Yokohama, Japan 2025. \\
 \item \textbf{Carrera, Dashiel}. ``Expressive HCXAI: An Art-Science Design Framework for Ethical and Usable AI System," HCXAI CHI Workshop. Honolulu, HI 2024. \\
  \item \textbf{Carrera, Dashiel}, Soden, Robert, Daniel Wigdor. ``Beyond Intelligence: Finding New Metaphors for AI through a Collaborative Workshop with Artists and Scholars" Towards Mutual Benefit: Reflecting on Artist Residencies as a Method for Collaboration, DIS Workshop. Pittsburgh, PA 2023. \\
   \item  Dietz, Paul H, \textbf{Carrera, Dashiel}, Alford, Gienr Jenifer, Cornelius, Abbie, Brockman, Jay, and Daniel Wigdor. ``Elementary Paper Animatronics" SIGGRAPH Workshop. Los Angeles, CA 2023. \\
  \item \textbf{Carrera, Dashiel}, Ovienmhada, Ufuoma, Hussein, Safa, and Robert Soden. ``Roadmap to Abolition: A Counter-mapping Project to Advance Understanding of the Theory and Practice of Abolition" In There is No Justice, Just US, CHI Worksop. New Orleans, LA 2022. 
  \end{enumerate}
  
%\subsection{Other}
%\begin{enumerate}
%\item \textbf{Carrera, Dashiel}. ``Finding the Missing Departments: Topic Modeling in the Harvard Course Catalog" In Harvard's metaLab medium. Cambridge, MA, 2017.\\
%\end{enumerate} 



