 \section{ACADEMIC TALKS}
 
 \begin{enumerate}
 
    \item \emph{Artist and Research Seminar}, Hong Kong University of Science and Technology, Hong Kong, Summer 2025. \subitem Hour long talk about my research and artistic practice for HKUST's new Arts and Machine Creativity program. 
 
   \item \emph{Nabokov's Cards and Electronic Literature}, Toronto, ON, Summer 2025. \subitem Gave talk about bottom-up creative writing application at Electronic Literature Conference. 
 
  \item \emph{Nabokov's Cards and Electronic Literature}, Toronto, ON, Summer 2025. \subitem Gave talk about bottom-up creative writing application at Electronic Literature Conference. 

   \item \emph{Nabokov's Cards: An LLM-Assisted Co-Writing System to Support Bottom-Up
Creative Writing}, London, UK, Summer 2025. \subitem Gave talk about bottom-up creative writing application at Creativity \& Cognition Conference. 
   
   \item \emph{Nabokov's Cards and Bhalpe}, Paris, France, Summer 2025. \subitem Gave talk about bottom-up creative writing application at conference on the work of Jean-Pierre Balpe. 
 
  \item \emph{Toronto Water Atlas Design Workshop}, Toronto, ON, Spring 2025. \subitem Led workshop for the Toronto Water Atlas workshop to help environmentalists understand role of narrative and aesthetic impact in design of digital maps that reveal role of water in Toronto communities. 
 
 \item \emph{Algancholy: Disappointment in the Face of AI Generated Art}, Toronto, ON, Spring 2025. \subitem Commissioned talk for Royal Conservatory of Music on why we feel disappointed when we learn a work is AI generated. 
 
  \item  \emph{Evaluating Interactive Arts}, Atlanta, GA, Winter 2025. \subitem Led conversation on how "awe" can be evaluated in interactive art and how it may be of use for HCI practitioners.
  
 \item  \emph{AI and the Future of Literature}, Mississauga, ON, Winter 2025. \subitem Commissioned talk about how AI will effect literature and creative writing at Sheridan College's Creative Writing Program; demoed AI co-writing tool Nabokov's Cards.
 
 \item  \emph{AI Metaphors Workshop}, Toronto, ON, Fall 2024. \subitem Led workshop that brought together 10 literary and digital media artists from Toronto to make artwork that interrogates alternative metaphors for AI.
  
 \item \emph{Future Careers Panel for Computer Science Undergrads}, Toronto, ON, Fall 2023. \textbf{(Invited Panelist)}  \subitem Gave talk about my unusual career path and career opportunities inside and outside of academia for undergraduates.
 
 \item  \emph{The Unseen Landscape of Abolitionism: Examining the Role of Digital Maps in Grassroots Organizing}, Minneapolis, MN, Fall 2023. \subitem Gave talk about paper investigating how digital mapping tools can support grassroots organizers. \\
 
 \item  \emph{Beyond Intelligence: Finding New Metaphors for AI through a Collaborative Workshop with Artists and Scholars}, Pittsburgh, PA, Summer 2023. \subitem Gave talk about a planned workshop that puts artists and scholars in conversation about design metaphors for artificial intelligence. \\
	
	\item  \emph{We're Not Decorators: Fostering Interdisciplinary Exchange in STEM--Artist Collaborations}, Pittsburgh, PA, Summer 2023. \subitem Gave talk about art-stem residencies in tech organizations at Design of Interactive Systems. \\
 
 	\item  \emph{Watch Me Write: Revealing Creative Process with Writing Replay}, Venice, IT, Spring 2022. \subitem Gave talk about writing replay paper at Creativity \& Cognition Conference. \\
         
      \item  \emph{In2Writing Workshop: The First Workshop on Intelligent and Interactive Writing Assistants}, Dublin, IE, Spring 2022. \subitem Invited panelist about the future of writing fiction with AI-assisted writing.\\
      
      \item  \emph{The Power of Immersive Stories}, Blacksburg, VA, Spring 2021. \subitem Presented immersive 3D immersive retelling of Jorge Luis Borges story ``Zoolog\'ia Fantastica in the Mist at Immersive Stories workshop at Virginia Tech.  \\
      
      \item \emph{Intrepid: The Exploratory Word Processor}, Computers and Writing Conference, Lansing, Michigan, Summer 2019. \subitem Constructed \emph{Intrepid}, dynamic word processor which encourages students to write uninhibited through experimental features: hiding all text except for the current word being typed, text-to-speech in the process of writing.
      
      \item \emph{Intrepid: The Exploratory Word Processor}, Blue Ridge Corridors Conference, Blacksburg, VA. \hfill Fall 2019 \subitem Presented survey of student users of \emph{Intrepid}. \emph{Intrepid} was incorporated into Pakistani English classrooms following this presentation.
      
    \end{enumerate}