 \subsection{ACADEMIC}
 
School for Poetic Computation Scholarship, \$500  \\
Received scholarship from School for Poetic Computation for course ``Cellular Automata: Code Beyond Words."
 
Computer Science Departmental Fellowship, \$1355 CAD \\
For students in good academic standing. 
 
Entanglements Network 2023 \\
 Elected to global collective of interdisciplinary poets, scientists, artists, and scholars who forge innovative initiatives across poetry, science, and the arts, including Anne Walkdman, Raw Armantrout, Nick Montfort, and others. 

 Massey College Junior Fellowship 2023 \\
 Elected Junior Fellow at Massey College, a cross-disciplinary community at University of Toronto. One of 20 accepted for resident fellowship.  
 
 ACM SIGCHI Gary Mardsen Travel Award 2022, \$1390  \\
Received travel grant to present paper ``Watch Me Write: Revealing Creative Process with Writing Replay" at Creativity \& Cognition in Venice, Italy.
 
University of Toronto School of Cities Grant 2022, \$500CAD \\
Received grant to perform interview study with prison and police abolitionists in North America on their concerns and desires for visibility in digital mapping tools.

University of Toronto Mississauga Travel Grant 2022, \$2500 CAD \\
Received travel grant to present paper ``Watch Me Write: Revealing Creative Process with Writing Replay" at Creativity \& Cognition in Venice, Italy.

University of California, Santa Cruz Chancellor's Award 2022, \$30,000 (declined) \\
UCSC's highest fellowship honor. Awarded to PhD applicants by nomination from department and selection of Graduate Council.

University of Toronto Graduate Research Fellowship, Department of Computer Science 2021, \$26,229 CAD per year \\
Fully funded to conduct Human-Computer Interaction research at the University of Toronto through a research fellowship. 

MIT Feminist Future Hackathon 2021, \$500 \\
Received stipend to participate in month-long social justice hackathon at MIT. 


National Merit Finalist 2011 \\
Given to top 1\% of PSAT scorers nationally with an outstanding high school academic record. 

National Merit Hispanic Scholar 2011 \\
Given to top PSAT scorers nationally who identify as Hispanic or Latinx. 