\section{PROFESSIONAL CREATIVE PRACTICE + TECHNICAL SKILLS}

\subsection{Audio Engineering \& Sound Design}
\begin{itemize}
  \item Multitrack recording, editing, and mixing for music and spoken word.
  \item Audio engineering and editing for podcasts (e.g., MFAngle Podcast).
  \item Foley recording and sound design for short film and video (e.g., \emph{The Toymaker}).
  \item Studio recording and session engineering (e.g., Digital Bear Entertainment).
  \item Live and broadcast audio for radio programming (e.g., WBRU Local Music Director).
\end{itemize}

\subsection{Interactive Media \& Installation Development}
\begin{itemize}
  \item Design and implementation of interactive sound installations and ambient systems (e.g., \emph{SoundClouds} at Goat Farm Arts Center).
  \item Development of immersive 3D narrative environments (e.g., \emph{Zoolog\'ia Fantastica in the Mist} at Moss Art Center).
  \item Creation of interactive public light exhibits and festival pieces (e.g., Wellington LUX Light Festival).
  \item Experience with sensor-driven and computer vision based interaction (Max/MSP, OpenCV, Arduinos).
\end{itemize}

\subsection{Creative Coding \& Web Development}
\begin{itemize}
  \item Front-end and creative web development for digital literature and media art (JavaScript, HTML, CSS).
  \item Development of interactive web-based storytelling and visualization (e.g., Three.js projects such as \emph{Zoolog\'ia Fantastica in the Mist}).
  \item Building and maintaining project and journal websites (e.g., \emph{The New River: A Journal of Digital Art and Literature}).
  \item Experience with rapid prototyping of interactive tools and interfaces for research and art.
\end{itemize}

\subsection{Data Science \& Computational Methods}
\begin{itemize}
  \item Data analysis and visualization in Python (Pandas, NumPy, SciPy, Jupyter Notebook).
  \item Computational methods for literary analysis and digital humanities (e.g., topic modeling and text analysis).
  \item Experimental design and A/B testing for HCI and learning research.
\end{itemize}

\subsection{Editorial \& Literary Practice}
\begin{itemize}
  \item Long-term editorial and curatorial work in contemporary literature and digital art (e.g., \textbf{Conjunctions} Assistant Editor).
  \item Digital and managing editor roles for electronic literature and hybrid-genre journals (e.g., \emph{The New River}, \emph{The Minnesota Review}).
  \item Manuscript and contest reading for innovative, cross-genre literary presses (e.g., Noemi Press, Hart House Literary Contest).
  \item Experience shaping and evaluating fiction, poetry, hybrid work, and digital literature for publication.
\end{itemize}
