 \subsection{ARTISTIC}
Entanglements Network 2023 \\
 Elected to global collective of interdisciplinary poets, scientists, artists, and scholars who forge innovative initiatives across poetry, science, and the arts, including Anne Walkdman, Raw Armantrout, Nick Montfort, and others. 
 
 International Initiative Grant 2023, \$450  \\
Received additional funding to display \emph{Zoolog\'ia Fantastica in the Mist} downtown to promote international learning and cross-cultural empathy. 
 
 Institute for Creativity, Arts, and Technology Student Seed Grant 2019, \$1000  \\
Interactive 3D model and bilingual storytelling adaptation of Jorge Luis Borges's \emph{Zoolog\'ia Fantastica} projected onto fog. (Three.js, Logic, Ableton)

New Media Writing Student Writing Prize 2018, Finalist\\
For ``Victoria Park Found Dead at 45," an expansive network of faux-NYTimes obituaries, funeral testimonials, videos, music, and interactive electronic literature. 

Dzanc Book Prize 2018, Longlist \\
For novel manuscript \emph{The Deer}, out September 2022 from Dalkey Archive Press.

Virginia Tech Graduate Teaching Fellowship 2018, \$20,700 per year \\
Fully funded for Masters of Fine Arts in Creative Writing through a teaching fellowship.

Brown University Creative Arts Council Grant 2014, \$1000 \\
Customized light waterfall pattern generated based on ID swipe mapped realtime to RGB NeoPixels. (Processing, Arduino)

HackPrinceton Crowd Favorite 2013, \$1000 \\
Received prize for creation of PersonalRave, a mask which maps the light intensity in the surrounding environment to a series of secondary colors for the wearer of the mask. (Arduino)

HackCooper 2nd Place 2011, \$666  \\
HighFrequencyStrealing: 2 player speed reaction game where every round the loser automatically makes a small Venmo transfer to the loser. (Arduino, Processing, GoogleAppEngine, Python)

Emily Morrison Prize in Poetry 2020, 1st Place,  \$1000  \\
Judged by Magdalena Zurawski who said, ``A fraught surrealism deftly assembles these imagistic poems into landscapes of failed psychic escapes."

WXIN Rock Hunt 2016, 1st Place, \$1000  \\
Received grand prize of \$1000 for winning Providence battle of the bands with my band Feng Shui Police.









 

