% \subsection{ARTISTIC PUBLICATIONS}


 \section{NOVELS}
\subsection{\emph{The Deer}. Dalkey Archive Press, 2022. }

\begin{itemize}
  \item Reviews: \emph{Chicago Review of Books}, \emph{Brooklyn Rail}, \emph{Publishers Weekly}
  \item Excerpts: \emph{Lit Hub}, \emph{The Offing}, \emph{FENCE}, \emph{3AM Magazine}
  \item Interviews and features: \emph{BOMB}, \emph{Los Angeles Review of Books}, \emph{Hazlitt}
  \item Book tour: Unnameable Books (Brooklyn), AWP (LA, Kansas, Seattle), Type Books (Toronto), McNally Jackson (NYC)
\end{itemize}
	
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}

\section{SHORT PUBLICATIONS}

 \begin{enumerate}
 
 
\subsubsection{Short Fiction}
\item \textbf{Carrera, Dashiel} ``The Opera Singer", LARB Quarterly, July 2025. \\
\item \textbf{Carrera, Dashiel} ``Salud, La Luz", LARB Quarterly, October 2023. \\
%\item \textbf{Carrera, Dashiel} ``from The Deer", Brooklyn Rail, September 2022. \\
%\item \textbf{Carrera, Dashiel} ``Excerpt from The Deer", The Offing, September 2022. \\
%\item \textbf{Carrera, Dashiel} ``Excerpt: The Deer", Literary Hub, August 2022. \\
%\item \textbf{Carrera, Dashiel} ``Decoherence", FENCE, August 2022. \\
%\item \textbf{Carrera, Dashiel} ``Wave Collapse", 3:AM Magazine, July 2022. \\


\subsubsection{New Media}
\item Bertram, Lillian-Yvonne, \textbf{Carrera, Dashiel}, ``RawGirlMoney", objkt.com, 2023.
\item \textbf{Carrera, Dashiel} ``The Deer: New Media Adaptation" In The New River: A Journal of Digital Art and Literature, Blacksburg, VA, 2019.\\

\subsubsection{Non Fiction}

\item \textbf{Carrera, Dashiel}  ``The Trump Neuron: AI and the Caricaturized Image" In Los Angeles Review of Books, Los Angeles, CA, 2026. (forthcoming)\\

\item \textbf{Carrera, Dashiel}  ``Algancholy and Its Discontents" In Los Angeles Review of Books, Los Angeles, CA, 2026. (forthcoming)\\

\item \textbf{Carrera, Dashiel}, B\"ok, Christian, Catanzano, Amy, Montfort, Nick, Katy Gero. ``Making a Literary Future with Artificial Intelligence" In Los Angeles Review of Books, Los Angeles, CA, 2026. (forthcoming)\\

\item \textbf{Carrera, Dashiel} ``White Noise, White Heat, White Books" In Los Angeles Review of Books, Los Angeles, CA, 2025.\\

\item \textbf{Carrera, Dashiel} ``Onto the Grayness: Christian B\"ok on The Xenotext" In Los Angeles Review of Books, Los Angeles, CA, 2025.\\

\item \textbf{Carrera, Dashiel} ``The Matador Waits " In Los Angeles Review of Books, Los Angeles, CA, 2025.\\

\item \textbf{Carrera, Dashiel} ``The Empty Spotlight: On Nicolette Polek's Bitter Water Opera " In Los Angeles Review of Books, Los Angeles, CA, 2024.\\

%\item \textbf{Carrera, Dashiel} ``Anchor Points and Improvisations: a Conversation Between Jeff Jackson and Dashiel Carrera " In Los Angeles Review of Books, Los Angeles, CA, 2023.\\
%\item \textbf{Carrera, Dashiel} ``Every Manner of Horror is Just a Google Search Away " In Hazlitt, Toronto, ON, 2022.\\
\item \textbf{Carrera, Dashiel} ``The Scent of Light " In Rain Taxi, Minneapolis, MN, 2022.\\
%
%\item \textbf{Carrera, Dashiel} and Blake Butler ``Sentences as Rhizomes: A Conversation " In BOMB Magazine, Brooklyn, NY, 2022.\\
%\item \textbf{Carrera, Dashiel}  ``Writing By Ear: Dashiel Carrera Interviewed" In X-R-A-Y Literary Magazine, 2022.\\
\item \textbf{Carrera, Dashiel}, Vollmer, Matthew, Tomkinson, Matthew, Carr, Julie, Jean Marc Ah-Sen. ``Five Writers on How Writing with Creative Constraints Unlocked Their Projects" In Literary Hub, New York City, New York, 2022.\\
%\item \textbf{Carrera, Dashiel}. ``Dashiel Carrera's Playlist for His Novel 'The Deer'" In largehearted boy, Brooklyn, New York, 2022.\\

\item \textbf{Carrera, Dashiel} ``The Water Vanishes: Alexandra Kleeman on \textit{Something New Under the Sun}, " In Los Angeles Review of Books, Los Angeles, CA, 2021.\\
\item \textbf{Carrera, Dashiel} ``Art and Futility: A Review of Juan Cardenas's \textit{Ornamental}, Translated by Lizzie Davis" In Los Angeles Review of Books, Los Angeles, CA, 2020.\\
\item \textbf{Carrera, Dashiel} ``Against the Grain: John O'Brien on the Possible Dalkey Archive/Open Letter Merger" In Los Angeles Review of Books, Los Angeles, CA, 2020. \\
\item \textbf{Carrera, Dashiel} Vipers, Robots, and Cheese Casseroles: Matthew Vollmer on \textit{Permanent Exhibit}, In Los Angeles Review of Books, Los Angeles, CA, 2018.\\
%\item \textbf{Carrera, Dashiel} When the Foam Settles: Essentialism in Tech, In The College Hill Independent, Providence, RI, 2015.\\
%\item \textbf{Carrera, Dashiel} The Perfect Bubble: The Polynomial Guide to the Universe, In The College Hill Independent, Providence, RI, 2015.\\
\end{enumerate}

%\subsection{Music}
%\textbf{Press}: Vanyaland, Providence Monthly, SpaceRockMountain, Providence Radio, Holy Crap Records Podcast, /r/indieheads      \\
%\begin{enumerate}
%\item \textbf{Carrera, Dashiel}, ``Simple EP", 75OrLessRecords, Providence, RI, 2021. \\
%\item \textbf{Carrera, Dashiel}, ``Plastic Astronauts LP", 75OrLessRecords, Providence, RI, 2018. \\
%\item \textbf{Carrera, Dashiel}, ``Plastic Astronauts EP", 75OrLessRecords, Providence, RI, 2017. \\
%\item \textbf{Carrera, Dashiel}, Harris, Evan, ``Graduation Sensation", 75OrLessRecords, Providence, RI, 2017. \\
%
%\item \textbf{Carrera, Dashiel}, Johnson, Hariz, Harris, Evan, ``Coffee with the Feng Shui Police EP", 75OrLessRecords, Providence, RI, 2015. \\
%        
%\item \textbf{Carrera, Dashiel}, Johnson, Hariz, Harris, Evan, ``Thank You EP", 75OrLessRecords, Providence, RI, 2015. \\
% \end{enumerate}

  




