\section{TALKS, PANELS, READINGS + PUBLIC EVENTS}

\begin{enumerate}

% ---------- 2026 ----------
\item \textbf{Panel} --- \emph{Naming the Unknown: A LARB Editor's Salon}, Los Angeles, CA, Spring 2026. 
\subitem Invited panelist with Gideon Jacobs, Jonathan Blake, Heidi Quante and Alicia Escott, hosted by Berggruen Institute.

\item \textbf{Panel} --- \emph{Center For Fiction: Making a Literary Future with AI}, Brooklyn, NY, Spring 2026. 
\subitem Panel with Bruce Holsinger and others on the future of fiction and AI. 

\item \textbf{Invited Talk} --- \emph{Artist and Research Seminar}, Pratt Institute, Manhattan, NY, Spring 2026. 
\subitem Hour-long talk about my research and artistic practice for Pratt Institute's School of Information.

\item \textbf{Reading} --- \emph{A Common Well Journal Reading}, Brooklyn, NY, Spring 2026. 
\subitem Reading for a Common Well Journal.
% ---------- 2025 ----------
\item \textbf{Reading} --- \emph{A Common Well Journal Presents: A Christmas Carol}, Manhattan, NY, Winter 2025.
\subitem Reading with Ashlie Atksinson, OF Cieri, Izzy Casey, and others.

\item \textbf{Conference Talk} --- \emph{Sound Clouds - Exploring ambient intelligence in
public spaces to elicit deep human experience of awe, wonder, and beauty.}, San Diego, ON, Winter 2025.
\subitem Presented Sound Clouds interaction sound media installation at NeurIPs Creative AI Track.

\item \textbf{Invited Talk} --- \emph{Artist and Research Seminar}, Hong Kong University of Science and Technology, Hong Kong, Summer 2025. 
\subitem Hour-long talk about my research and artistic practice for HKUST's new Arts and Machine Creativity program.

\item \textbf{Conference Talk} --- \emph{Nabokov's Cards and Electronic Literature}, Toronto, ON, Summer 2025.
\subitem Talk on bottom-up creative writing application at the Electronic Literature Conference.

\item \textbf{Conference Talk} --- \emph{Nabokov's Cards: An LLM-Assisted Co-Writing System}, London, UK, Summer 2025.
\subitem Presented research on LLM-assisted creative writing at Creativity \& Cognition.

\item \textbf{Conference Talk} --- \emph{Nabokov's Cards and Balpe}, Paris, France, Summer 2025.
\subitem Talk at conference on the work of Jean-Pierre Balpe.

\item \textbf{Reading} --- \emph{Patio Reading Series}, Manhattan, NY, Summer 2025.
\subitem Reading with Paula Bomer, Conor Truax, Donald Berger, and others.

\item \textbf{Reading} --- \emph{Entanglements Network + Ugly Duckling Press}, Los Angeles, CA, Spring 2025.
\subitem Reading with Amy Catanzano, Nick Montfort, Christian B\"ok, and others.

\item \textbf{Reading} --- \emph{Neon Night Mic Reading}, Los Angeles, CA, Spring 2025.
\subitem Reading with Kathryn Scanlan, Henry Hoke, Sawako Nagayasu, and others.

\item \textbf{Panel (Organizer)} --- \emph{AWP: Making a Literary Future with Artificial Intelligence}, Los Angeles, CA, Spring 2025.
\subitem Organized and moderated panel with Christian B\"ok, Amy Catanzano, Nick Montfort, and Katy Gero.

\item \textbf{Workshop Lead} --- \emph{Toronto Water Atlas Design Workshop}, Toronto, ON, Spring 2025.
\subitem Led workshop helping environmentalists understand narrative \& aesthetic impact in digital maps.

\item \textbf{Invited Talk} --- \emph{Algancholy: Disappointment in the Face of AI-Generated Art}, Royal Conservatory of Music, Toronto, ON, Spring 2025.
\subitem Commissioned talk on why people feel disappointment when art is revealed to be AI-generated.

\item \textbf{Reading} --- \emph{LostInTheLetters}, Atlanta, GA, Spring 2025.
\subitem Reading with Claire Batemen and Laura Jaramillo.

\item \textbf{Invited Talk} --- \emph{Evaluating Interactive Arts}, Atlanta, GA, Winter 2025.
\subitem Led discussion on evaluating ``awe'' in interactive art for HCI practitioners.

\item \textbf{Invited Talk} --- \emph{AI and the Future of Literature}, Sheridan College, Mississauga, ON, Winter 2025.
\subitem Commissioned talk on AI's impact on literature; demoed co-writing tool \emph{Nabokov's Cards}.

% ---------- 2024 ----------
\item \textbf{Workshop Lead} --- \emph{AI Metaphors Workshop}, Toronto, ON, Fall 2024.
\subitem Led workshop bringing together literary and digital media artists to design alternative AI metaphors.

\item \textbf{Reading} --- \emph{Type Books}, Toronto, ON, Fall 2024.
\subitem In conversation with Tracy O'Neill about her memoir \emph{Women of Interest}.

\item \textbf{Reading} --- \emph{Breadloaf Blue Parlor Series}, Ripton, VA, Summer 2024.
\subitem Reading series for Breadloaf Writers Conference participants.

\item \textbf{Reading} --- \emph{Chaveta Coffee Author Reading}, Toronto, Canada, Summer 2024.
\subitem Reading with Ken Sparling, Lily Wang, and Albert Koehl.

\item \textbf{Artist Talk} --- \emph{Artist / Researcher in Residence Talk}, UKAI Projects, Toronto, ON, Spring 2024.
\subitem Talk on liminality, AI voice agents, and performativity in writing.

\item \textbf{Reading} --- \emph{Babak Lakghomi Reading}, Toronto, Canada, Spring 2024.
\subitem Reading with Ken Sparling, Zach Davidson, and others.

\item \textbf{Craft Talk} --- \emph{Creative Constraints}, Edmonton Public Library, Edmonton, AB, Spring 2024.
\subitem Craft lecture on creative constraints for writers.

\item \textbf{Staged Reading} --- \emph{WordTheatre}, Manhattan, NY, Spring 2024.
\subitem Professional actor Lou Diamond Phillips performed my story ``Salud, La Luz.''

\item \textbf{Reading} --- \emph{BANFF Centre for Creative Arts}, Banff, AB, Winter 2024.
\subitem Reading presented during Banff residency.

% ---------- 2023 ----------
\item \textbf{Reading} --- \emph{Type Books}, Toronto, ON, Spring 2023.
\subitem In conversation with Tom Comitta about his novel \emph{The Nature Book}.

\item \textbf{Panel (Invited)} --- \emph{Future Careers Panel for Computer Science Undergrads}, Toronto, ON, Fall 2023.
\subitem Panelist discussing career paths inside/outside academia.

\item \textbf{Conference Talk} --- \emph{The Unseen Landscape of Abolitionism}, Minneapolis, MN, Fall 2023.
\subitem Presented research on digital mapping tools for grassroots organizers.

\item \textbf{Conference Talk} --- \emph{Beyond Intelligence: New Metaphors for AI}, Pittsburgh, PA, Summer 2023.
\subitem Talk on collaborative metaphor-design workshop for AI.

\item \textbf{Conference Talk} --- \emph{We're Not Decorators}, Pittsburgh, PA, Summer 2023.
\subitem Presented work on art--STEM residencies at DIS.

% ---------- 2022 ----------
\item \textbf{Conference Talk} --- \emph{Watch Me Write: Writing Replay}, Venice, IT, Spring 2022.
\subitem Presented at Creativity \& Cognition.

\item \textbf{Invited Panelist} --- \emph{In2Writing Workshop}, Dublin, IE, Spring 2022.
\subitem Panel on the future of intelligent writing assistants.

% ---------- 2021 ----------
\item \textbf{Talk} --- \emph{The Power of Immersive Stories}, Blacksburg, VA, Spring 2021.
\subitem Presented 3D interactive retelling of Borges's ``Zoolog\'ia Fantastica in the Mist.''

% ---------- 2019 ----------
\item \textbf{Conference Talk} --- \emph{Intrepid: The Exploratory Word Processor}, Lansing, MI, Summer 2019.
\subitem Presented experimental writing tool \emph{Intrepid} at Computers and Writing.

\item \textbf{Conference Talk} --- \emph{Intrepid: The Exploratory Word Processor}, Blacksburg, VA, Fall 2019.
\subitem Presented survey results; \emph{Intrepid} later adopted in Pakistani English classrooms.

\item \textbf{Interview} --- \emph{MFAngle Podcast}, Blacksburg, VA, Fall 2019.
\subitem Interview on navigating artistic process before/during MFA.

% ---------- 2021 ----------
\item \textbf{Festival Reading} --- \emph{Glossolalia Festival}, Blacksburg, VA, Spring 2021.
\subitem Reading of both poetry and fiction (competitive acceptance).

\end{enumerate}
