 
   \subsection{Installations}
  \begin{enumerate}
  
  \item \emph{The Deer}, Inter/Access, Toronto, ON, Spring 2025. \subitem Video art piece made from AI generated clips based on first chapter of novel The Deer with audio recitation and various audio embedded audio effects and foley. (Sora, Logic, Capcut)\\
  
   \item  \emph{SoundClouds}, Goat Farm Arts Center, Atlanta, GA, Spring 2025. \subitem Sound installation in which large scale helium inflatables are pushed around a room to modulate a surround sound scape. 200+ people attendees (Max / MSP, OpenCV, Arduinos)\\
   \item \emph{LuminAI}, High Museum, Atlanta, GA, Spring 2025. \subitem Artificial Intelligence literacy exhibit in which participants learn about AI by teaching an AI how to dance (Kinect, Unity) \\
    \item  \emph{Dialtone Disconnect}, UKAI Projects, Toronto, CA, Spring 2024. \subitem Sound installation piece with hanging telephone using AI generated voices trained on dial tones and samples of dialtones over the eras. (ElevenLabs, Logic)\\
  \item  \emph{Zoolog\'ia Fantastica in the Mist}, Moss Art Center, Blacksburg, VA, Spring 2020. \subitem Interactive 3D storytelling adaptation of Jorge Luis Borges's compilation of international fairy tales. (Three.js, Logic, Abelton)\\
  \item  \emph{Light Waterfall}, Brown University, Providence, RI, Spring 2014. \subitem Guerrilla install of a light waterfall that generates custom patterns based on swipe of student IDs. \\
\item  \emph{Moon Printer}, Granoff Center for the Arts, Brown University, Providence, RI, Spring 2014.\subitem  Receipt printer that printed a stream of the current moon phase every day for a month. \\
 \end{enumerate}
 
    \subsection{Artist Talks}
    \begin{enumerate}
    \item \emph{Artist / Researcher in Residence Talk}, UKAI Projects, Toronto, ON, Spring 2024. \subitem Talk about liminality, AI voice agents, and the performative dimension of writing. 
    \end{enumerate}
 
%% \subsection{Performances}
%% \begin{enumerate}
%% \item \emph{Death of a Poem: Live Writing Audiovisual Performance}, Electronic Literature Organization, University of Central Florida, Orlando, Florida, Summer 2020 (Cancelled for pandemic). \subitem Performance in which poem is composed live in front of an audience with dynamic temporal typography and sound effects.\\
%% \item \emph{The Deer: New Media Adaptation}, Electronic Literature Organization, University College Cork, Cork, Ireland, Summer 2019. \subitem Performed audio-visual adaptation of my novel \emph{The Deer}, later published by Dalkey Archive Press. \\
%% \item \emph{Sound of Space: An Interactive Afrofuturist Experience}, The Cube, Blacksburg, VA, Spring 2019. \subitem Co-directed interactive installation with Afrofuturist mixtapes and cyclorama projection in a 360 surround sound theater.  \\
%% \item \emph{Dashiel Carrera solo performance}, Firehouse 13, Providence, RI, Fall 2016. \subitem Performed solo set for 75OrLessRecords benefit gig.\\
%% \item \emph{Various Rock Performances}, (The Met, AS220, O'Brien's, The Parlour, News Cafe...), New England, 2014-2016. \subitem Performed over 30 paid performances with my punk band Feng Shui Police.\\
%% \item \emph{Practice}, Grant Recital Hall, Brown University, Providence, RI, Spring 2016. \subitem Performed improvised monologue with quadrophonic sound effects and sample overlays.\\
%% \item \emph{The Sabateur}, Grant Recital Hall, Brown University, Providence, RI, Spring 2016. \subitem Performed invented instruments made with Leap Motion, guitar, piano, and OSC connected iPads.\\
%% \item \emph{Bug Music}, Grant Recital Hall, Brown University, Providence, RI, Fall 2014. \subitem Performed music with automated toy bugs and contact mics.\\
%% \item \emph{Hex on Math}, Grant Recital Hall, Brown University, Providence, RI, \hfill Fall 2014.
%%\subitem Performed invented instrument made from circuit bent Speak and Math toy. \\
%%\end{enumerate}