    \subsection{Literary Events}
    \begin{enumerate}
    
    	\item \emph{Babak Lakghomi Reading}, Toronto, Canada, Spring 2024. \subitem Reading series with Ken Sparling,  Zach Davidson, and others.  \\
        \item \emph{Creative Constraints}, Edmonton, Alberta, Spring 2024. \subitem Craft talk on how creative constraints can unlock creative practice for Edmonton Public Library.   \\
    \item \emph{Unnameable Books}, Brooklyn, NY, Spring 2024. \subitem Reading as part of book tour for ``The Deer." \\
    \item \emph{WordTheatre}, Manhattan, NY, Spring 2024. \subitem Staged reading by professional actor of story ``Salud, La Luz.Œ" \\Œ
    \item \emph{AWP Signing}, Kansas City, MO, Winter 2024. \subitem Signing as part of book tour for ``The Deer." \\
      \item \emph{BANFF Centre for Creative Arts}, Banff, AB, Winter 2024. \subitem Reading as part of residency at BANFF Centre for Creative Arts. \\
    
    
    \item \emph{Type Books}, Toronto, ON, Spring 2023. \subitem In conversation with Tom Comitta about his novel ``The Nature Book." \\
    \item \emph{AWP Signing}, Seattle, WAS, Spring 2023. \subitem Signing as part of book tour for ``The Deer." \\
    \item \emph{Akimbo Bookstore}, Rochester, NY, Fall 2022. \subitem Reading as part of book tour for ``The Deer." \\
    \item \emph{Type Books}, Toronto, ON, Fall 2022.  \subitem Reading as part of book tour for ``The Deer." \\
     \item \emph{Third Place Books}, Virtual, Fall 2022.  \subitem Reading as part of book tour for ``The Deer." \\
    \item \emph{RiffRaff Bookstore}, Providence, RI, Fall 2022. \subitem Reading as part of book tour for ``The Deer." \\
    \item \emph{McNally Jackson Seaport}, Manhattan, NY, Fall 2022. \subitem Reading as part of book tour for ``The Deer." \\
    \item \emph{Blacksburg Books}, Blacksburg, VA, Fall 2022. \subitem Reading as part of book tour for ``The Deer." \\
      \item  \emph{Glossolalia Festival}, Blacksburg, VA, Spring 2021. \subitem Reading at literary festival, both poetry and fiction. Competitive acceptance. \\
  \item  \emph{MFAngle Podcast}, Blacksburg, VA, Fall 2019. \subitem Gave interview about navigating artistic process inside and outside of an MFA program.
 
 \end{enumerate}
