 \section{PRESS}
 \begin{enumerate}
   \item  \emph{A Review of The Deer by Dashiel Carrera}, The Collidescope, July 2023. \\
  \item  \emph{Sharp Edges of an Echo: A Review of Dashiel Carrera's The Deer}, Ancillary Review of Books, December 2022. \\
 \item  \emph{Favorite Authors (And their Books)}, NeonPajamas, December 2022. \\
\item  \emph{Michael J. Seidlinger \& Dashiel Carrera}, The Brooklyn Rail, September 2022. \\
\item  \emph{AMA Ñ Dashiel Carrera, author of THE DEER, forthcoming Dalkey Archive Press}, Reddit /r/TrueLit, August 2022. \\
\item  \emph{Sonic Pleasures in ``The Deer"}, Chicago Review of Books, August 2022. \\
 \item  \emph{In his first novel, graduate student Dashiel Carrera explores ``what it means to reckon with memory"}, Canada Today, July 2022. \\
 \item  \emph{In his first novel, graduate student Dashiel Carrera explores ``what it means to reckon with memory"}, UofT News, July 2022. \\
 \item  \emph{Schršdinger's Deer}, Biblioklept, July 2022. \\
\item  \emph{Morning Bites: Revisting James Welch, Dashiel Carrera Excerpted, Dwyer Murphy on Noir Fiction, and More}, Vol1 Brooklyn, July 2022. \\
\item  \emph{Book Reviews by Conor Hultman: ``The Deer" by Dashiel Carrera}, The Local Voice, July 2022. \\ 
 \item  \emph{Review of The Deer}, Publisher's Weekly, June 2022. \\
\item  \emph{Deep Vellum to Relaunch Dalkey Archive in April 2022}, Publisher's Weekly, November 2021. \\
\item \emph{Deep Vellum will relaunch the Dalkey Archive this April}, LitHub, November 2021.\\
\item \emph{Weirdos in a Band Drinking Coffee}, Providence Monthly, December 2015.\\
\item \emph{Song Premiere: Providence's Feng Shui Police burst with youthful energy on 'Try'}, Vanyaland, September 2015.\\
\item \emph{EP Grab Bag Vol. 93}, SpaceRockMountain, March 2015.

\end{enumerate}
 
 